---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# survextras

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of survextras is to provide helper functions for survival analysis.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("alberto-mateos-mo/survextras")
```

The package contains 3 main functions:

- `intro_surv()`
- `max_diff_time()`
- `parametric_diagnose()`

## Example

`intro_surv()` function will give you an introductory plot of your survival data:

```{r example, warning=FALSE}
library(survextras)
library(survival)

intro_surv(df = cancer, times = "time", event = "status", interactive = FALSE)
```

`max_diff_time()` function finds and plots maximun difference time fitted survival curves.

```{r, warning=FALSE}
library(survextras)
library(survival)
library(survminer)

fit <- surv_fit(Surv(time, status)~sex, data = cancer)
max_diff_time(fit)
```

`parametric_diagnose()` function creates assesment plot to diagnose if KM estimator could potentially follow a known distribution.

```{r, warning=FALSE}
library(survextras)
library(survival)
library(survminer)

kmfit <- surv_fit(Surv(time, status)~1, data = cancer)
parametric_diagnose(kmfit)
```

